other functionalities

### 2019-08-07 inst/gitbook/05_other-functionalities.Rmd
Added vignette

## `slide.nodes`

@@

>>>>

## `slide.nodes` and `remove.zero.brlen`

@@

The `remove.zero.brlen` is a "clever" wrapping function that uses the `slide.nodes` function to stochastically remove zero branch lengths across a whole tree.
This function will slide nodes up or down in successive postorder traversals (i.e. going down the tree clade by clade) in order to minimise the number of nodes to slide while making sure there are no silly negative branch lengths produced!
By default it is trying to slide the nodes using 1% of the minimum branch length to avoid changing the topology too much.

```{r}
set.seed(42)
## Generating a tree
tree <- rtree(20)

## Adding some zero branch lengths (5)
tree$edge.length[sample(1:Nedge(tree), 5)] <- 0

## And now removing these zero branch lengths!
tree_no_zero <- remove.zero.brlen(tree)

## Exaggerating the removal (to make it visible)
tree_exaggerated <- remove.zero.brlen(tree, slide = 1)

## Check the differences
any(tree$edge.length == 0)
any(tree_no_zero$edge.length == 0)
any(tree_exaggerated$edge.length == 0)

## Display the results
par(mfrow = c(3,1))
plot(tree, main = "with zero edges")
plot(tree_no_zero, main = "without zero edges!")
plot(tree_exaggerated, main = "with longer edges")
```
